VIPE: Virtualized Intermittently-Powered Executor

### 2017-07-19 paper/background.tex
corrections on section the type of computing HW

>>>>

\subsection{Assumption on the Type of Computing Hardware}
\label{sec:background_hardware}

We assume that we operate on the microcontroller (more generally, computing hardware) equipped with a mix of volatile and non-volatile memory, such as FLASH, Ferroelectric RAM or Magnetoresistive RAM. \sys does not assume to rely on specific memory type (either volatile or non-volatile), in contrary to earlier works targeting non-volatile processors~\cite{su_date_2017,ratchet,quickrecall,nvp}. Actually, \sys will exploit the properties of both memory types to maximize performance metrics of the program being executed. We make \sys able to I/O operations, however we do not enable the scheduling of operations (which \emph{nota bene} forms a foundation for a simple runtime). All in all, our hardware model follows in assumptions the two most relevant intermittently-powered execution environments~\cite{alpaca,chain}.
